\documentclass[]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[USenglish]{babel}
\usepackage{microtype, multicol, marginnote, bera, parskip}
\usepackage{listings, amsmath, amssymb, graphicx, tikz, epic}
\usepackage{stmaryrd} %for lightning arrow
\usepackage[babel=true]{csquotes}
\tolerance=2000
\setcounter{secnumdepth}{0}

\usetheme{Hannover}
\usecolortheme{seahorse}

\author{Nils Döring \and Michael Mardaus  \and Sebastian Müller \and Julian F. Rost}
\title{Critical view on cloud computing}

\begin{document}

\begin{frame}
        \titlepage
\end{frame}

%\begin{frame}
%        \frametitle{Structure}
%        \framesubtitle{What you are up to}
%        \tableofcontents[hideallsubsections]
%\end{frame}

\section{Gain}

\begin{frame}
        \frametitle{Gains for different groups}
        \framesubtitle{Winner and Prices}
        \begin{center}
        Who is gaining and how?
        \end{center}
\end{frame}

\subsection{Cloud-Owners}

\begin{frame}
        \frametitle{Gains for different groups}
        \framesubtitle{Cloud-Owners}
        \begin{itemize}
                \item higher utilization of the existing computing power
                \item lower average costs for bigger systems
                \item additional income for companies from other sectors
        \end{itemize}
\end{frame}

\subsection{Cloud-Users}

\begin{frame}
        \frametitle{Gains for different groups}
        \framesubtitle{Cloud-Users}
        \begin{itemize}
                \item easier access to computing resources
                \item "scalable" resources
        \end{itemize}
\end{frame}

\subsection{Governments}

\begin{frame}
        \frametitle{Gains for different groups}
        \framesubtitle{Governments}
        \begin{itemize}
                \item means for censorship and prosecution (Youtube and
                Pakistan, USA-Patriot-Act, "Great Firewall of China",
                BKA-"Stop-Signs")
        \end{itemize}
\end{frame}

\section{Challenges}

\begin{frame}
        \frametitle{Challenges of using clouds}
        \framesubtitle{Obstacles and hurdles}
        What are we up to, if we consider to use a cloud-service?
\end{frame}

\subsection{Performance}

\begin{frame}
        \frametitle{Performance challenges}
        \framesubtitle{Is it as fast as yesterday?}
        \begin{itemize}
                \item varying performance - especially in smaller and medium sized
                clouds {load-changes have higher impact}
                \item latency might cause trouble with timeouts
        \end{itemize}
\end{frame}

\subsection{Accessibility}

\begin{frame}
        \frametitle{Accessibility/dependence challenges}
        \framesubtitle{Why can't I connect and when is it fixed?}
        \begin{itemize}
                \item as data and service is outsourced, connection has to be
                highly-available
                \item need for outage prevention and mitigation
        \end{itemize}
\end{frame}

\subsection{Strategic}

\begin{frame}
        \frametitle{Strategic challenges}
        \framesubtitle{How much do you want to pay for what?}
        \begin{itemize}
                \item low-cost solution vs. better or more secure solutions
                (aka. Finance Dept. vs. IT Dept.)
                \item outsourcing of know-how
                \item lock-in might be more expensive in the long run (raising
                prices)
                \item need for strict auditing
                \item more complex communication between cloud-provider and
                cloud-users
        \end{itemize}
\end{frame}

\subsection{Modifiability}

\begin{frame}
        \frametitle{Modifiability challenges}
        \framesubtitle{Your code is perfect, now change it!}
        \begin{itemize}
                \item given standardized protocols and software-versions
                \item monopolization of standards
                \item scalability is limited by the architecture of the cloud
                \item long-term SLAs might slow down development
        \end{itemize}
\end{frame}

\subsection{Customer-Relationship}

\begin{frame}
        \frametitle{Customer-Relationship challenges}
        \framesubtitle{What to tell on press-conferences?}
        \begin{itemize}
                \item is the company allowed to store customers data in the
                cloud?
                \item are customers expecting the data to be stored inhouse?
        \end{itemize}
\end{frame}

\section{Risks}

\begin{frame}
        \frametitle{Risks for all participants}
        \framesubtitle{What can go wrong, will go wrong?}
       \begin{center}
        Which problems and dangers might occur?
       \end{center}
\end{frame}

\subsection{Privacy}

\begin{frame}
        \frametitle{Privacy risks}
        \framesubtitle{My data, your data, our data!}
        \begin{itemize}
                \item need for complete encryption to protect privacy, slows
                down computation
                \item laws for privacy regulation might hinder services
                \item national security regulations can prevent privacy
                \item other cloud-users share the same hardware, thus it is
                easier to get access to protected data
                \item cloud-owners can access your data nearby as they wish
        \end{itemize}
\end{frame}

\subsection{Integrity}

\begin{frame}
        \frametitle{Integrity risks}
        \framesubtitle{I am sure, I've checked that!}
        \begin{itemize}
                \item since the processes are virtualized or layered, there are
                no guaranties for integrity of data or procedures
                \item possible loss of data, if the cloud-provider does not take
                care
        \end{itemize}
\end{frame}

\subsection{Reachability}

\begin{frame}
        \frametitle{Reachability risks}
        \framesubtitle{Why is the internet offline?}
        \begin{itemize}
                \item a cloud-service without connectivity is useless
                \item lower bandwidth inhibits effective use of services
                \item permanent connection is necessary, each breakdown hurts
                public-relations
        \end{itemize}
\end{frame}

\subsection{Security}

\begin{frame}
        \frametitle{Security risks}
        \framesubtitle{Once my machine, now your machine!}
        \begin{itemize}
                \item each security breach affects the whole cloud
                \item broken and taken over cloud-users could infect or
                slow-down the whole cloud
                \item standardized hardware and software-stacks are preferred
                targets
        \end{itemize}
\end{frame}

\subsection{Social}

\begin{frame}
        \frametitle{Social risks}
        \framesubtitle{Some are more equal than others!}
        \begin{itemize}
                \item cloud-computing leads to the centralizing of the Internet
                \item regions without broadband-connectivity are excluded from
                cloud-usage
                \item monopolists push other companies out of the market
                \item computation-power concentrates on a few players
                \item know-how concentrates also on a few players
        \end{itemize}
\end{frame}

\section{Paper}

\begin{frame}
        \frametitle{Paper}
        \framesubtitle{Where to look at}
        \begin{itemize}
                \item Security and high availability in cloud computing
                environments - IBM (2011)
                \item Emerging Issues: Cloud Computing 1 of 5- South African Internet
                Governance (2011)
                \item Above the Clouds: A Berkeley View of Cloud Computing
                (2009)
        \end{itemize}
\end{frame}

\end{document}
